---
title-meta: sirf
execute:
  warning: false
  echo: false
  message: false
format:
  typst:
    keep-typ: true
  pdf:
    keep-md: true
    keep-tex: true
params:
  pheno: "g"
  return_plot: TRUE
---

```{r}
#| label: make-g
#| include: false

scales <- c(
  "Academic Skills",
  "Attention",
  "Attention/Executive",
  "Attentional Fluency",
  "Cognitive Efficiency",
  # "Cognitive Proficiency",
  # "Crystallized Knowledge",
  "Delayed Recall",
  # "Executive Functions",
  "Fluency",
  # "Fluid Reasoning",
  # "General Ability",
  "Learning Efficiency",
  # "Memory",
  "Planning",
  # "Processing Speed",
  "Psychomotor Speed",
  "Verbal/Language",
  "Visual Perception/Construction",
  "Working Memory"
)

g <-
  readxl::read_excel("index_scores.xlsx") |>
  janitor::clean_names() |>
  dplyr::mutate(z = (index - 100) / 15) |>
  dplyr::filter(composite_name %in% scales) |>
  dplyr::filter(!is.na(z))

# extra for now
write.csv(g, paste("g_v2.csv"), row.names = FALSE)
```

```{r}
#| label: fig-domain-plot
#| column: page
#| fig-cap: "Overall neurocognitive function subdomain plots of #patient's strengths and weaknesses. *Note:* *z*-scores have a mean of 0 and a standard deviation of 1."

pheno <- "g"
data <- g
x <- g$z
y <- g$composite_name
colors <- NULL
return_plot <- TRUE
filename <- "fig_g.svg"

bwu::dotplot(
  data = g,
  x = x,
  y = y,
  colors = colors,
  return_plot = return_plot,
  filename = filename
)
```


## Summary and Formulation

- Alexandra's difficulties in areas like attention could make tasks like reading a book, watching a movie, or following a conversation quite challenging.
- Her challenges with planning might mean she struggles with activities that require forethought, such as organizing a trip or managing a project.
- A below average organization skill could manifest in a disorganized living space, missed appointments, or difficulty managing work or school assignments.
- With her working memory being below average, Alexandra might forget instructions soon after they're given or struggle to follow multi-step processes.
- Her struggle with initiation can be a major hurdle in daily life – she might find it hard to start tasks, whether it's a simple chore or a significant project.
- Emotion regulation issues can lead to disproportionate reactions to minor issues, which might strain personal or professional relationships.

Conclusion:
While Alexandra exhibits strengths in some areas, she faces significant challenges in key domains of executive functioning. It would be beneficial for her to seek interventions or coping strategies to manage these challenges, especially given their potential impact on her daily life and well-being.

In daily life, Alexandra's strengths in word fluency and reasoning will assist
in organizing information and problem-solving. However, she may struggle when
required to rapidly generate words or in noisy environments.

## AT/EF

Overall, Alexandra demonstrates strengths, notably in working memory, strategic
planning, and problem-solving. While her performance across several domains is average, she shows a
slight lag in psychomotor speed, which could influence certain daily tasks
requiring rapid coordination, such as quickly jotting down notes, typing, or
performing fast repetitive actions. 

Biggie is a 28-year-old left-handed female with a history of medically refractory epilepsy who was referred for neuropsychological testing as part of a comprehensive presurgical work-up. General cognitive ability is well within normal limits, and there is no evidence of decline from premorbid estimates. No deficits were detected in the domains of attention, processing speed, motor functioning, or visuospatial skills. Although many aspects of executive functioning, language functioning, and memory were within normal limits, she demonstrated mildly inefficient problem solving and hypothesis testing, weaknesses in word retrieval, and inefficiency in new learning of verbal information. There is no evidence of a mood disorder at this time.

In conclusion, the cognitive profile is mildly localizing and lateralizing as there are elements that suggest relative left temporal involvement. That said, there were features seen during testing that suggested mild frontal systems disruption as well.
Although Biggie lives alone, she has arranged to have her mother stay with her for a week or two after surgery to help her and provide support in the immediate postacute period. She seems to have a good understanding of and appropriate expectations for the surgery. Taken together with her current asymptomatic mood profile, there are no obvious psychological risk factors for a poor outcome or need for presurgical mental health intervention.

### Diagnostic Impression

- 314.01 (F90.2) Attention-Deficit/Hyperactivity Disorder (ADHD), Combined
  Presentation
- [DSM-5/ICD-10 Codes](03.01_dsm5_icd10_dx.md)
