---
title: "Pluck Tables from WISC-5"
params:
  patient: Brooklyn
  test: wisc5
  test_name: WISC-5
  file:
    label: "No file selected"
    value: file
    input: file
  pages: [22, 23, 26, 29, 30]
  table1:
    label: "Subtest Score Summary"
    value: [Similarities, Vocabulary, Block Design, Matrix Reasoning, Figure Weights, Digit Span, Picture Span, Coding, Symbol Search]
    input: select
    multiple: yes
    choices:
      Verbal Comprehension (VCI):
        - Similarities
        - Vocabulary
        - Information
        - Comprehension
      Visual Spatial (VSI):
        - Block Design
        - Visual Puzzles
      Fluid Reasoning (FRI):
        - Matrix Reasoning
        - Figure Weights
        - Picture Concepts
        - Arithmetic
      Working Memory (WMI):
        - Digit Span
        - Picture Span
        - Letter-Number Sequencing
      Processing Speed (PSI):
        - Coding
        - Symbol Search
        - Cancellation
  table2:
    label: "Composite Score Summary"
    value: [Verbal Comprehension (VCI), Fluid Reasoning (FRI), Working Memory (WMI), Processing Speed (PSI), Full Scale IQ (FSIQ)]
    input: select
    multiple: yes
    choices:
      - Verbal Comprehension (VCI)
      - Visual Spatial (VSI)
      - Fluid Reasoning (FRI)
      - Working Memory (WMI)
      - Processing Speed (PSI)
      - Full Scale IQ (FSIQ)
  table3:
    label: "Ancillary Composite Scores"
    value: [General Ability (GAI), Cognitive Proficiency (CPI)]
    input: select
    multiple: yes
    choices:
      - Verbal (Expanded Crystallized) (VECI)
      - Expanded Fluid (EFI)
      - Quantitative Reasoning (QRI)
      - Auditory Working Memory (AWMI)
      - Nonverbal (NVI)
      - General Ability (GAI)
      - Cognitive Proficiency (CPI)
      - Naming Speed (NSI)
      - Symbol Translation (STI)
      - Storage & Retrieval (SRI)
  table4:
    label: "Total Raw Score to Scaled Score Conversion"
    value: [Block Design No Time Bonus, Digit Span Forward, Digit Span Backward, Digit Span Sequencing]
    input: select
    multiple: yes
    choices:
      - Block Design No Time Bonus
      - Block Design Partial Score
      - Digit Span Forward
      - Digit Span Backward
      - Digit Span Sequencing
      - Cancellation Random
      - Cancellation Structured
  table5:
    label: "Total Raw Score to Base Rate Conversion"
    value: [Longest Digit Span Forward, Longest Digit Span Backward, Longest Digit Span Sequencing]
    input: select
    multiple: yes
    choices:
      - Longest Digit Span Forward
      - Longest Digit Span Backward
      - Longest Digit Span Sequencing
      - Longest Picture Span Stimulus
      - Longest Picture Span Response
      - Longest Letter-Number Sequence
      - Block Design Dimension Errors
      - Block Design Rotation Errors
      - Coding Rotation Errors
      - Symbol Search Set Errors
      - Symbol Search Rotation Errors
      - Naming Speed Literacy Errors
      - Naming Speed Quantity Errors
  colnames1: [domain, scale, abbrev, raw_score, score, percentile, age_equiv, sem]
  colnames2: [scale, abbrev, raw_score, score, percentile, ci_95, category, sem]
  colnames3:
    label: "Table 4 Column Names"
    value: [scale, abbrev, raw_score, score]
  colnames4:
    label: "Table 5 Column Names"
    value: [scale, abbrev, raw_score, base_rate]
  keep1:
    label: "Variables to Keep, Set 1"
    value: [scale, raw_score, score, percentile, age_equiv]
  keep2:
    label: "Variables to Keep, Set 2"
    value: [scale, raw_score, score, percentile, ci_95]
output:
  rmdformats::robobook:
    highlight: kate
---

## Load libraries

```{r setup, include = FALSE}
Sys.setenv(
  JAVA_HOME =
    "/Library/Java/JavaVirtualMachines/graalvm-community-openjdk-22.0.1+8.1/Contents/Home"
)
options(java.parameters = "-Xmx16000m")
knitr::opts_chunk$set(
  root.dir = normalizePath("./"),
  echo = TRUE,
  message = TRUE,
  warning = FALSE,
  error = TRUE
)
library(collapse)
library(dplyr)
library(hablar)
library(here)
library(knitr)
library(magrittr)
library(purrr)
library(readr)
library(rJava)
library(rmarkdown)
library(rmdformats)
library(qs)
library(shiny)
library(snakecase)
library(tabulapdf)
library(tibble)
library(tidyr)
library(tidyverse)
library(bwu)
```

## Parameters

```{r}
patient <- params$patient
test <- params$test
test_name <- params$test_name
pages <- params$pages
# file <- file.path(file.choose())
# file <- file.path(params$file)
# qs::qsave(file, paste0(test, "_path.rds"))
# file <- qs::qread(paste0(test, "_path.rds"))
```

## Extract Areas

```{r}
# This works well so far
# areas_wisc5 <- tabulapdf::extract_areas(
#   file = file,
#   pages = pages
# )
# 
# areas_wisc5 <- tabulapdf::locate_areas(
#   file = file,
#   pages = pages
# )
# areas <- areas_wisc5
# Save the entire list to an R data file
# qs::qsave(areas, file = "areas_wisc5.rds")
areas <- qs::qread("~/Brooklyn/src/rmd/areas_wisc5.rds")
```

## Extract tables

```{r}
plucked_tables <- tabulapdf::extract_tables(
  file = file,
  pages = pages,
  area = areas,
  method = "stream",
  output = "matrix",
  guess = FALSE
)
```

```{r}
# Save the entire list to an R data file
# qs::qsave(plucked_tables, file = "plucked_tables_wisc5.rds")
plucked_tables <- qs::qread("plucked_tables_wisc5.rds")
```

## Function process_wisc_tables

```{r}
library(dplyr)
library(purrr)

process_wisc_tables <- function(plucked_tables) {
  table_list <- purrr::map(plucked_tables, as_tibble) %>%
    set_names(paste0("table", 1:length(plucked_tables))) # Rename tables

  list2env(table_list, .GlobalEnv) # Assign to global environment
}

# Example Usage:
process_wisc_tables(plucked_tables)

# Loop over the list and write each matrix to a CSV file
for (i in seq_along(plucked_tables)) {
  write.csv(plucked_tables[[i]], file = paste0(test, "_", i, ".csv"), row.names = FALSE)
}
```

# Table 1

## Change scale names

```{r}
names(table1) <- params$colnames1
table1 <- table1[3:18, 2:8]
table1[1, 1] <- c("Similarities")
table1[2, 1] <- c("Vocabulary")
table1[3, 1] <- c("Information")
table1[4, 1] <- c("Comprehension")
table1[5, 1] <- c("Block Design")
table1[6, 1] <- c("Visual Puzzles")
table1[7, 1] <- c("Matrix Reasoning")
table1[8, 1] <- c("Figure Weights")
table1[9, 1] <- c("Picture Concepts")
table1[10, 1] <- c("Arithmetic")
table1[11, 1] <- c("Digit Span")
table1[12, 1] <- c("Picture Span")
table1[13, 1] <- c("Letter-Number Sequencing")
table1[14, 1] <- c("Coding")
table1[15, 1] <- c("Symbol Search")
table1[16, 1] <- c("Cancellation")
table1 <- table1 |> dplyr::select(all_of(params$keep1))
```

## Extract rows with data

```{r}
library(dplyr)

# Function to replace "-" with NA and filter out rows with no real data
filter_real_data <- function(table, key_columns) {
  table <- table %>%
    mutate(across(all_of(key_columns), ~ if_else(. == "-", NA_character_, as.character(.)))) %>%
    mutate(across(all_of(key_columns), as.numeric)) %>%
    filter(rowSums(is.na(select(., all_of(key_columns)))) < length(key_columns))

  return(table)
}

# Assuming key_columns are those columns which must have data
key_columns <- c("raw_score", "score", "percentile")

# Extract and filter table1
table1_all_rows <- as_tibble(table1) # Ensure table1 is a tibble
table1 <- filter_real_data(table1_all_rows, key_columns)

# Print the filtered table
print(table1)

```

## Mutate/Ranges

```{r}
table1 <- bwu::gpluck_make_columns(
  table1,
  test = params$test,
  test_name = params$test_name,
  ci_95 = "",
  range = "",
  domain = "",
  subdomain = "",
  narrow = "",
  pass = "Sequential",
  verbal = "Verbal",
  timed = "Untimed",
  test_type = "npsych_test",
  score_type = "scaled_score",
  description = "",
  result = ""
)

# Test score ranges
table1 <- bwu::gpluck_make_score_ranges(
  table = table1,
  test_type = "npsych_test"
)
```

## Domains/Subdomains

```{r}
# Domain
table1 <-
  table1 |>
  dplyr::mutate(
    domain = dplyr::case_when(
      scale == "Similarities" ~ "Verbal/Language",
      scale == "Vocabulary" ~ "Verbal/Language",
      scale == "Information" ~ "Verbal/Language",
      scale == "Comprehension" ~ "Verbal/Language",
      scale == "Block Design" ~ "Visual Perception/Construction",
      scale == "Visual Puzzles" ~ "Visual Perception/Construction",
      scale == "Matrix Reasoning" ~ "Visual Perception/Construction",
      scale == "Figure Weights" ~ "Visual Perception/Construction",
      scale == "Picture Concepts" ~ "Visual Perception/Construction",
      scale == "Arithmetic" ~ "Attention/Executive",
      scale == "Digit Span" ~ "Attention/Executive",
      scale == "Picture Span" ~ "Attention/Executive",
      scale == "Letter-Number Sequencing" ~ "Attention/Executive",
      scale == "Coding" ~ "Attention/Executive",
      scale == "Symbol Search" ~ "Attention/Executive",
      scale == "Cancellation" ~ "Attention/Executive",
      TRUE ~ as.character(domain)
    )
  )

# Subdomain
table1 <-
  table1 |>
  dplyr::mutate(
    subdomain = dplyr::case_when(
      scale == "Similarities" ~ "Reasoning",
      scale == "Vocabulary" ~ "Knowledge",
      scale == "Information" ~ "Knowledge",
      scale == "Comprehension" ~ "Reasoning",
      scale == "Block Design" ~ "Construction",
      scale == "Visual Puzzles" ~ "Visualization",
      scale == "Matrix Reasoning" ~ "Reasoning",
      scale == "Figure Weights" ~ "Reasoning",
      scale == "Picture Concepts" ~ "Reasoning",
      scale == "Arithmetic" ~ "Working Memory",
      scale == "Digit Span" ~ "Working Memory",
      scale == "Picture Span" ~ "Working Memory",
      scale == "Letter-Number Sequencing" ~ "Working Memory",
      scale == "Coding" ~ "Processing Speed",
      scale == "Symbol Search" ~ "Processing Speed",
      scale == "Cancellation" ~ "Attention",
      TRUE ~ as.character(subdomain)
    )
  )

# Narrow
table1 <-
  table1 |>
  dplyr::mutate(
    narrow = dplyr::case_when(
      scale == "Similarities" ~ "Word Reasoning",
      scale == "Vocabulary" ~ "Word Knowledge",
      scale == "Information" ~ "General World Knowledge",
      scale == "Comprehension" ~ "Acquired Knowledge",
      scale == "Block Design" ~ "Block Construction",
      scale == "Visual Puzzles" ~ "Visualization",
      scale == "Matrix Reasoning" ~ "Nonverbal Reasoning",
      scale == "Figure Weights" ~ "Quantitiative Reasoning",
      scale == "Picture Concepts" ~ "Nonverbal Reasoning",
      scale == "Arithmetic" ~ "Verbal Working Memory",
      scale == "Digit Span" ~ "Verbal Working Memory",
      scale == "Picture Span" ~ "Nonverbal Working Memory",
      scale == "Letter-Number Sequencing" ~ "Verbal Working Memory",
      scale == "Coding" ~ "Cognitive Efficiency",
      scale == "Symbol Search" ~ "Perceptual Speed",
      scale == "Cancellation" ~ "Attentional Fluency",
      TRUE ~ as.character(narrow)
    )
  )

# PASS Model
table1 <-
  table1 |>
  dplyr::mutate(
    pass = dplyr::case_when(
      scale == "Block Design" ~ "Simultaneous",
      scale == "Visual Puzzles" ~ "Simultaneous",
      scale == "Matrix Reasoning" ~ "Simultaneous",
      scale == "Figure Weights" ~ "Simultaneous",
      scale == "Picture Concepts" ~ "Simultaneous",
      scale == "Arithmetic" ~ "Attention",
      scale == "Digit Span" ~ "Attention",
      scale == "Picture Span" ~ "Attention",
      scale == "Letter-Number Sequencing" ~ "Attention",
      scale == "Cancellation" ~ "Attention",
      scale == "Coding" ~ "Planning",
      scale == "Symbol Search" ~ "Planning",
      TRUE ~ as.character(pass)
    )
  )

## Verbal vs Nonverbal
table1 <-
  table1 |>
  dplyr::mutate(
    verbal = dplyr::case_when(
      scale == "Block Design" ~ "Nonverbal",
      scale == "Visual Puzzles" ~ "Nonverbal",
      scale == "Matrix Reasoning" ~ "Nonverbal",
      scale == "Figure Weights" ~ "Nonverbal",
      scale == "Picture Concepts" ~ "Nonverbal",
      scale == "Arithmetic" ~ "Verbal",
      scale == "Digit Span" ~ "Verbal",
      scale == "Picture Span" ~ "Nonverbal",
      scale == "Letter-Number Sequencing" ~ "Verbal",
      scale == "Cancellation" ~ "Nonverbal",
      scale == "Coding" ~ "Nonverbal",
      scale == "Symbol Search" ~ "Nonverbal",
      TRUE ~ as.character(verbal)
    )
  )

## Timed vs Untimed
table1 <-
  table1 |>
  dplyr::mutate(
    timed = dplyr::case_when(
      scale == "Block Design" ~ "Timed",
      scale == "Visual Puzzles" ~ "Timed",
      scale == "Matrix Reasoning" ~ "Untimed",
      scale == "Figure Weights" ~ "Timed",
      scale == "Picture Concepts" ~ "Untimed",
      scale == "Arithmetic" ~ "Timed",
      scale == "Digit Span" ~ "Untimed",
      scale == "Picture Span" ~ "Untimed",
      scale == "Letter-Number Sequencing" ~ "Untimed",
      scale == "Cancellation" ~ "Timed",
      scale == "Coding" ~ "Timed",
      scale == "Symbol Search" ~ "Timed",
      TRUE ~ as.character(timed)
    )
  )
```

## Scale descriptions

```{r}
table1 <-
  table1 |>
  dplyr::mutate(
    description = dplyr::case_when(
      scale ==
        "Similarities" ~ "Verbal inductive reasoning",
      scale ==
        "Vocabulary" ~ "Word/lexical knowledge",
      scale ==
        "Information" ~ "Acquired knowledge/ability to acquire, retain, and retrieve general factual knowledge",
      scale ==
        "Comprehension" ~ "Practical knowledge and judgment of general principles and social situations",
      scale ==
        "Block Design" ~ "Understanding visual-spatial relationships to construct geometric designs from a model",
      scale ==
        "Visual Puzzles" ~ "Generate visual images in the mind's eye",
      scale == "Matrix Reasoning" ~ "Inductive reasoning and nonverbal problem-solving",
      scale == "Figure Weights" ~ "General sequential (deductive) reasoning and quantitative reasoning",
      scale == "Picture Concepts" ~ "Reasoning and semantic matching",
      scale == "Arithmetic" ~ "Solving math word problems in working memory",
      scale == "Digit Span" ~ "Registering, maintaining, and manipulating auditory information",
      scale == "Picture Span" ~ "Maintenance and resequencing of progressively lengthier sets of pictures in spatial working memory",
      scale == "Letter-Number Sequencing" ~ "Maintenance and resequencing of progressively lengthier number and letter strings in working memory",
      scale == "Coding" ~ "Efficiency of psychomotor speed, visual scanning ability, and visual-motor coordination",
      scale == "Symbol Search" ~ "Visual-perceptual decision-making speed",
      scale == "Cancellation" ~ "Selective visual attention, visual discrimination, and visual-perceptual processing",
      TRUE ~ as.character(description)
    )
  )
```

## Glue results

```{r}
table1 <-
  table1 %>%
  dplyr::mutate(
    result = glue::glue(
      "{description} was {range}.\n"
    )
  )

## Relocate variables
table1 <- table1 |> dplyr::relocate(c(raw_score, score, ci_95, percentile, range), .after = scale)

table1 <- table1 |> dplyr::relocate(c(test, test_name), .before = scale)
```

# Table 2

## Change scale names

```{r}
names(table2) <- params$colnames2
table2 <- table2[4:9, ]
table2[1, 1] <- c("Verbal Comprehension (VCI)")
table2[2, 1] <- c("Visual Spatial (VSI)")
table2[3, 1] <- c("Fluid Reasoning (FRI)")
table2[4, 1] <- c("Working Memory (WMI)")
table2[5, 1] <- c("Processing Speed (PSI)")
table2[6, 1] <- c("Full Scale IQ (FSIQ)")
table2 <- table2 |> dplyr::select(all_of(params$keep2))
```

## Extract rows with data

```{r}
library(dplyr)

# Function to replace "-" with NA and filter out rows with no real data
filter_real_data <- function(table, key_columns) {
  table <- table %>%
    mutate(across(all_of(key_columns), ~ if_else(. == "-", NA_character_, as.character(.)))) %>%
    mutate(across(all_of(key_columns), as.numeric)) %>%
    filter(rowSums(is.na(select(., all_of(key_columns)))) < length(key_columns))

  return(table)
}

# Assuming key_columns are those columns which must have data
key_columns <- c("raw_score", "score", "percentile")

# Extract and filter table2
table2_all_rows <- as_tibble(table2)
table2 <- filter_real_data(table2_all_rows, key_columns)

# Print the filtered table
print(table2)
```

## Mutate columns

```{r}
table2 <- bwu::gpluck_make_columns(
  table2,
  test = params$test,
  test_name = params$test_name,
  ci_95 = "",
  range = "",
  domain = "General Cognitive Ability",
  subdomain = "",
  narrow = "",
  pass = "Sequential",
  verbal = "Verbal",
  timed = "Untimed",
  test_type = "npsych_test",
  score_type = "standard_score",
  description = "",
  result = ""
)

# Test score ranges
table2 <- bwu::gpluck_make_score_ranges(
  table = table2,
  test_type = "npsych_test"
)
```

## Domains/Subdomains

```{r}
# Subdomain
table2 <-
  table2 |>
  dplyr::mutate(
    subdomain = dplyr::case_when(
      scale == "Verbal Comprehension (VCI)" ~ "Crystallized Knowledge",
      scale == "Visual Spatial (VSI)" ~ "Visuospatial Processing",
      scale == "Fluid Reasoning (FRI)" ~ "Fluid Reasoning",
      scale == "Working Memory (WMI)" ~ "Working Memory",
      scale == "Processing Speed (PSI)" ~ "Processing Speed",
      scale == "Full Scale IQ (FSIQ)" ~ "General Intelligence",
      TRUE ~ as.character(subdomain)
    )
  )

# Narrow
table2 <-
  table2 |>
  dplyr::mutate(
    narrow = dplyr::case_when(
      scale == "Verbal Comprehension (VCI)" ~ "Crystallized Knowledge",
      scale == "Visual Spatial (VSI)" ~ "Visuospatial Processing",
      scale == "Fluid Reasoning (FRI)" ~ "Fluid Reasoning",
      scale == "Working Memory (WMI)" ~ "Working Memory",
      scale == "Processing Speed (PSI)" ~ "Processing Speed",
      scale == "Full Scale IQ (FSIQ)" ~ "General Intelligence",
      TRUE ~ as.character(narrow)
    )
  )

## Verbal vs Nonverbal

table2 <-
  table2 |>
  dplyr::mutate(
    verbal = dplyr::case_when(
      scale == "Verbal Comprehension (VCI)" ~ "Verbal",
      scale == "Visual Spatial (VSI)" ~ "Nonverbal",
      scale == "Fluid Reasoning (FRI)" ~ "Nonverbal", # unless arithmetic too
      scale == "Working Memory (WMI)" ~ "",
      scale == "Processing Speed (PSI)" ~ "Nonverbal",
      scale == "Full Scale IQ (FSIQ)" ~ "",
      TRUE ~ as.character(verbal)
    )
  )

## Timed vs Untimed
table2 <-
  table2 |>
  dplyr::mutate(
    timed = dplyr::case_when(
      scale == "Verbal Comprehension (VCI)" ~ "Untimed",
      scale == "Visual Spatial (VSI)" ~ "Timed",
      scale == "Fluid Reasoning (FRI)" ~ "",
      scale == "Working Memory (WMI)" ~ "Untimed",
      scale == "Processing Speed (PSI)" ~ "Timed",
      scale == "Full Scale IQ (FSIQ)" ~ "",
      TRUE ~ as.character(timed)
    )
  )
```

## Descriptions

```{r}
table2 <-
  table2 |>
  dplyr::mutate(
    description = dplyr::case_when(
      scale == "Verbal Comprehension (VCI)" ~ "Verbal Comprehension (i.e., the ability to verbalize meaningful concepts, think about verbal information, and express oneself using words)",
      scale == "Visual Spatial (VSI)" ~ "Visual Spaital is not an independent factor",
      scale == "Fluid Reasoning (FRI)" ~ "Fluid Reasoning (i.e., the ability to use reasoning to identify and apply solutions to problems)",
      scale == "Working Memory (WMI)" ~ "Verbal and nonverbal working memory skills",
      scale == "Processing Speed (PSI)" ~ "Processing speed, psychomotor speed, and cognitive efficiency",
      scale == "Full Scale IQ (FSIQ)" ~ "General Intelligence (*g*)",
      scale == "General Ability (GAI)" ~ "A subset of intellectual functioning with reduced influences of working memory and processing speed",
      TRUE ~ as.character(description)
    )
  )
```

## Glue result

```{r}
table2 <-
  table2 |>
  dplyr::mutate(
    result = dplyr::case_when(
      scale == "Verbal Comprehension (VCI)" ~ glue::glue(
        "{description} was classified as {range} and ranked at the {percentile}th percentile.\n"
      ),
      scale == "Visual Spatial (VSI" ~ glue::glue(
        "{description} was classified as {range} and ranked at the {percentile}th percentile.\n"
      ),
      scale == "Fluid Reasoning (FRI)" ~ glue::glue(
        "{description} was classified as {range} and ranked at the {percentile}th percentile.\n"
      ),
      scale == "Working Memory (WMI)" ~ glue::glue(
        "{description} fell in the {range} range.\n"
      ),
      scale == "Processing Speed (PSI)" ~ glue::glue(
        "{description} was {range}.\n"
      ),
      scale == "Full Scale IQ (FSIQ)" ~ glue::glue(
        "{description} was {range} overall.\n"
      ),
      scale == "General Ability (GAI)" ~ glue::glue(
        "{description} was {range} and ranked at the {percentile}th percentile, indicating performance as good as or better than {percentile}% of same-age peers from the general population.\n"
      ),
      TRUE ~ as.character(result)
    )
  )

## Relocate variables
table2 <- table2 |> dplyr::relocate(c(raw_score, score, ci_95, percentile, range), .after = scale)

table2 <- table2 |> dplyr::relocate(c(test, test_name), .before = scale)
```

# Table 3

## Change scale names

```{r}
names(table3) <- params$colnames2

table3 <- table3[c(6, 8:13), ]

table3[1, 1] <- c("Verbal (Expanded Crystallized) (VECI)")
table3[2, 1] <- c("Expanded Fluid (EFI)")
table3[3, 1] <- c("Quantitative Reasoning (QRI)")
table3[4, 1] <- c("Auditory Working Memory (AWMI)")
table3[5, 1] <- c("Nonverbal (NVI)")
table3[6, 1] <- c("General Ability (GAI)")
table3[7, 1] <- c("Cognitive Proficiency (CPI)")
# table3[1, 1] <- c("Naming Speed (NSI)")
# table3[2, 1] <- c("Symbol Translation (STI)")
# table3[3, 1] <- c("Storage & Retrieval (SRI)")

table3 <- table3 |> dplyr::select(all_of(params$keep2))
```

## Extract rows with data

```{r}
# Extract and filter table3
table3_all_rows <- as_tibble(table3)
table3 <- filter_real_data(table3_all_rows, key_columns)

# Print the filtered table
print(table3)
```

## Mutate columns

```{r}
table3 <- bwu::gpluck_make_columns(
  table3,
  test = params$test,
  test_name = params$test_name,
  ci_95 = "",
  range = "",
  domain = "General Cognitive Ability",
  subdomain = "",
  narrow = "",
  pass = "",
  verbal = "",
  timed = "",
  test_type = "npsych_test",
  score_type = "standard_score",
  description = "",
  result = ""
)

# Test score ranges
table3 <- bwu::gpluck_make_score_ranges(
  table = table3,
  test_type = "npsych_test"
)
```

## Domains/Subdomains

```{r}
table3 <-
  table3 |>
  mutate(
    domain = case_when(
      ## Ancillary
      scale == "Verbal (Expanded Crystallized) (VECI)" ~ "General Cognitive Ability",
      scale == "Expanded Fluid (EFI)" ~ "General Cognitive Ability",
      scale == "Quantitative Reasoning (QRI)" ~ "General Cognitive Ability",
      scale == "Auditory Working Memory (AWMI)" ~ "Attention/Executive",
      scale == "Nonverbal (NVI)" ~ "General Cognitive Ability",
      scale == "General Ability (GAI)" ~ "General Cognitive Ability",
      scale == "Cognitive Proficiency (CPI)" ~ "Attention/Executive",
      ## Complementary
      scale == "Naming Speed (NSI)" ~ "Verbal/Language",
      scale == "Symbol Translation (STI)" ~ "Memory",
      scale == "Storage & Retrieval (SRI)" ~ "Memory",
      TRUE ~ as.character(domain)
    )
  )

# Subdomain
table3 <-
  table3 |>
  mutate(
    subdomain = case_when(
      scale == "General Ability (GAI)" ~ "General Intelligence",
      scale == "Cognitive Proficiency (CPI)" ~ "Executive Functioning",
      scale == "Auditory Working Memory (AWMI)" ~ "Working Memory",
      scale == "Expanded Fluid (EFI)" ~ "Fluid Intelligence",
      scale == "Nonverbal (NVI)" ~ "Fluid Intelligence",
      scale == "Quantitative Reasoning (QRI)" ~ "Fluid Intelligence",
      scale == "Verbal (Expanded Crystallized) (VECI)" ~ "Crystallized Intelligence",
      scale == "Naming Speed (NSI)" ~ "Retrieval Fluency",
      scale == "Symbol Translation (STI)" ~ "Learning Efficiency",
      scale == "Storage & Retrieval (SRI)" ~ "Long-Term Storage and Retrieval",
      TRUE ~ as.character(subdomain)
    )
  )

# Narrow
table3 <-
  table3 |>
  mutate(
    narrow = case_when(
      scale == "Auditory Working Memory (AWMI)" ~ "Verbal Working Memory",
      scale == "Cognitive Proficiency (CPI)" ~ "Cognitive Efficiency",
      scale == "Expanded Fluid (EFI)" ~ "Fluid Intelligence",
      scale == "General Ability (GAI)" ~ "General Intelligence",
      scale == "Nonverbal (NVI)" ~ "Fluid Intelligence",
      scale == "Quantitative Reasoning (QRI)" ~ "Quantitative Reasoning",
      scale == "Verbal (Expanded Crystallized) (VECI)" ~ "Crystallized Intelligence",
      scale == "Naming Speed (NSI)" ~ "Naming Facility",
      scale == "Storage & Retrieval (SRI)" ~ "Retrieval Fluency",
      scale == "Symbol Translation (STI)" ~ "Learning Efficiency",
      TRUE ~ as.character(narrow)
    )
  )

# PASS Model
table3 <-
  table3 |>
  mutate(
    pass = case_when(
      scale == "General Ability (GAI)" ~ "",
      scale == "Cognitive Proficiency (CPI)" ~ "",
      scale == "Nonverbal (NVI)" ~ "Simultaneous",
      scale == "Auditory Working Memory (AWMI)" ~ "Sequential",
      scale == "Expanded Fluid (EFI)" ~ "Simultaneous",
      scale == "Quantitative Reasoning (QRI)" ~ "Simultaneous",
      scale == "Verbal (Expanded Crystallized) (VECI)" ~ "Sequential",
      scale == "Naming Speed (NSI)" ~ "Attention",
      scale == "Storage & Retrieval (SRI)" ~ "Simultaneous",
      scale == "Symbol Translation (STI)" ~ "Simultaneous",
      TRUE ~ as.character(pass)
    )
  )

## Verbal vs Nonverbal
table3 <-
  table3 |>
  mutate(
    verbal = case_when(
      scale == "Auditory Working Memory (AWMI)" ~ "Verbal",
      scale == "Cognitive Proficiency (CPI)" ~ "",
      scale == "Expanded Fluid (EFI)" ~ "Nonverbal",
      scale == "General Ability (GAI)" ~ "",
      scale == "Nonverbal (NVI)" ~ "Nonverbal",
      scale == "Quantitative Reasoning (QRI)" ~ "",
      scale == "Verbal (Expanded Crystallized) (VECI)" ~ "Verbal",
      scale == "Naming Speed (NSI)" ~ "Verbal",
      scale == "Storage & Retrieval (SRI)" ~ "Verbal",
      scale == "Symbol Translation (STI)" ~ "Nonverbal",
      TRUE ~ as.character(verbal)
    )
  )

## Timed vs Untimed
table3 <-
  table3 |>
  mutate(
    timed = case_when(
      scale == "Auditory Working Memory (AWMI)" ~ "Untimed",
      scale == "Cognitive Proficiency (CPI)" ~ "Timed",
      scale == "Expanded Fluid (EFI)" ~ "Untimed",
      scale == "General Ability (GAI)" ~ "Untimed",
      scale == "Nonverbal (NVI)" ~ "Timed",
      scale == "Quantitative Reasoning (QRI)" ~ "Timed",
      scale == "Verbal (Expanded Crystallized) (VECI)" ~ "Untimed",
      scale == "Naming Speed (NSI)" ~ "Timed",
      scale == "Storage & Retrieval (SRI)" ~ "Timed",
      scale == "Symbol Translation (STI)" ~ "Untimed",
      TRUE ~ as.character(timed)
    )
  )
```

## Scale descriptions

```{r}
table3 <-
  table3 |>
  mutate(
    description = case_when(
      ## Ancillary
      scale == "Verbal (Expanded Crystallized) (VECI)" ~ "Verbal concept formation, verbal reasoning, verbal comprehension and expression, acquired knowledge, and practical knowledge and judgment (expanded)",
      scale == "Expanded Fluid (EFI)" ~ "The ability to use reasoning to identify and apply solutions to problems (expanded)",
      scale == "Quantitative Reasoning (QRI)" ~ "Quantitative reasoning skills",
      scale == "Auditory Working Memory (AWMI)" ~ "Auditory working memory processes supported by the phonological loop; ability to register, maintain, and manipulate verbally-presented information",
      scale == "Nonverbal (NVI)" ~ "General intellectual functioning that minimizes expressive language demands",
      scale == "General Ability (GAI)" ~ "A subset of intellectual functioning with reduced influences of working memory and processing speed",
      scale == "Cognitive Proficiency (CPI)" ~ "An index of cognitive processing proficiency that reduces crystallzied knowledge, verbal reaoning, and fluid reasoning demands",
      ## Complementary
      scale == "Naming Speed (NSI)" ~ "Automaticity of naming",
      scale == "Symbol Translation (STI)" ~ "An index of visual-verbal associative memory",
      scale == "Storage & Retrieval (SRI)" ~ "The ability to accurately and efficiently store and retrieve auditory and visual information fromlong-term memory",
      TRUE ~ as.character(description)
    )
  )

# ranges
table3 <-
  table3 %>%
  dplyr::mutate(
    result = glue::glue(
      "{description} was {range}.\n"
    )
  )

## Relocate variables
table3 <- table3 |> dplyr::relocate(c(raw_score, score, ci_95, percentile, range), .after = scale)
table3 <- table3 |> dplyr::relocate(c(test, test_name), .before = scale)
```

# Tables 4-5

## Change scale names

```{r}
# Table 4
names(table4) <- params$colnames3
table4 <- table4[2:8, c(1,3:4)]
table4[1, 1] <- c("Block Design No Time Bonus")
table4[2, 1] <- c("Block Design Partial Score")
table4[3, 1] <- c("Digit Span Forward")
table4[4, 1] <- c("Digit Span Backward")
table4[5, 1] <- c("Digit Span Sequencing")
table4[6, 1] <- c("Cancellation Random")
table4[7, 1] <- c("Cancellation Structured")

# Table 5
names(table5) <- params$colnames4
table5 <- table5[2:14, c(1,3:4)]
table5[1, 1] <- c("Longest Digit Span Forward")
table5[2, 1] <- c("Longest Digit Span Backward")
table5[3, 1] <- c("Longest Digit Span Sequence")
table5[4, 1] <- c("Longest Picture Span Stimulus")
table5[5, 1] <- c("Longest Picture Span Response")
table5[6, 1] <- c("Longest Letter-Number Sequence")
table5[7, 1] <- c("Block Design Dimension Errors")
table5[8, 1] <- c("Block Design Rotation Errors")
table5[9, 1] <- c("Coding Rotation Errors")
table5[10, 1] <- c("Symbol Search Set Errors")
table5[11, 1] <- c("Symbol Search Rotation Errors")
table5[12, 1] <- c("Naming Speed Literacy Errors")
table5[13, 1] <- c("Naming Speed Quantity Errors")
```

## Extract rows with data

```{r}
# Removed percentile
key_columns <- c("raw_score", "score")
# Extract and filter table4
table4_all_rows <- as_tibble(table4)
table4 <- filter_real_data(table4_all_rows, key_columns)
# Print the filtered table
print(table4)
```

```{r}
# Removed percentile
key_columns <- c("raw_score")
# Extract and filter table5
table5_all_rows <- as_tibble(table5)
table5 <- filter_real_data(table5_all_rows, key_columns)
# Print the filtered table
print(table5)
```

## Mutate columns

```{r}
table4 <- bwu::gpluck_make_columns(
  table4,
  range = "",
  ci_95 = "",
  test = params$test,
  test_name = params$test_name,
  domain = "Attention/Executive",
  subdomain = "Working Memory",
  narrow = "",
  pass = "Attention",
  verbal = "Verbal",
  timed = "Untimed",
  test_type = "npsych_test",
  score_type = "scaled_score",
  description = "",
  result = ""
)

table5 <- bwu::gpluck_make_columns(
  table5,
  range = "",
  test = params$test,
  test_name = params$test_name,
  domain = "Attention/Executive",
  subdomain = "",
  narrow = "",
  pass = "",
  verbal = "",
  timed = "",
  test_type = "npsych_test",
  score_type = "raw_score",
  description = "",
  result = ""
)
```

## Compute percentile for table 4

```{r}
table4 <- bwu::gpluck_compute_percentile_range(
  .x = table4,
  .score = table4$score,
  .score_type = "scaled_score"
)
```

## Test score ranges

```{r}
table4 <- bwu::gpluck_make_score_ranges(
  table = table4,
  test_type = "npsych_test"
)
```

```{r}
library(dplyr)

table4 <-
  table4 |>
  dplyr::mutate(
    domain = dplyr::case_when(
      ## Total Raw Score to Scaled Score Conversion
      scale == "Block Design No Time Bonus" ~ "Visual Perception/Construction",
      scale == "Block Design Partial Score" ~ "Visual Perception/Construction",
      scale == "Digit Span Backward" ~ "Attention/Executive",
      scale == "Digit Span Forward" ~ "Attention/Executive",
      scale == "Digit Span Sequencing" ~ "Attention/Executive",
      scale == "Cancellation Random" ~ "Attention/Executive",
      scale == "Cancellation Structured" ~ "Attention/Executive",
      TRUE ~ as.character(domain)
    )
  )

table5 <-
  table5 |>
  mutate(
    domain = case_when(
      ## Total Raw Score to Base Rate Conversion
      scale == "Longest Digit Span Backward" ~ "Attention/Executive",
      scale == "Longest Digit Span Forward" ~ "Attention/Executive",
      scale == "Longest Digit Span Sequence" ~ "Attention/Executive",
      scale == "Longest Picture Span Response" ~ "Attention/Executive",
      scale == "Longest Picture Span Stimulus" ~ "Attention/Executive",
      scale == "Longest Letter-Number Sequence" ~ "Attention/Executive",
      scale == "Block Design Dimension Errors" ~ "Visual Perception/Construction",
      scale == "Block Design Rotation Errors" ~ "Visual Perception/Construction",
      scale == "Coding Rotation Errors" ~ "Attention/Executive",
      scale == "Symbol Search Set Errors" ~ "Attention/Executive",
      scale == "Symbol Search Rotation Errors" ~ "Attention/Executive",
      scale == "Naming Speed Literacy Errors" ~ "Verbal/Language",
      scale == "Naming Speed Quantity Errors" ~ "Verbal/Language",
      TRUE ~ as.character(domain)
    )
  )

table4 <-
  table4 |>
  mutate(
    subdomain = case_when(
      scale == "Block Design No Time Bonus" ~ "Construction",
      scale == "Block Design Partial Score" ~ "Construction",
      scale == "Digit Span Forward" ~ "Attention",
      scale == "Digit Span Backward" ~ "Working Memory",
      scale == "Digit Span Sequencing" ~ "Working Memory",
      scale == "Cancellation Random" ~ "Processing Speed",
      scale == "Cancellation Structured" ~ "Processing Speed",
      TRUE ~ as.character(subdomain)
    )
  )

table5 <-
  table5 |>
  mutate(
    subdomain = case_when(
      scale == "Block Design Dimension Errors" ~ "Response Monitoring",
      scale == "Block Design Rotation Errors" ~ "Response Monitoring",
      scale == "Coding Rotation Errors" ~ "Response Monitoring",
      scale == "Longest Digit Span Backward" ~ "Working Memory",
      scale == "Longest Digit Span Forward" ~ "Attention Span",
      scale == "Longest Digit Span Sequence" ~ "Working Memory",
      scale == "Longest Letter-Number Sequence" ~ "Working Memory",
      scale == "Longest Picture Span Response" ~ "Working Memory",
      scale == "Longest Picture Span Stimulus" ~ "Working Memory",
      scale == "Naming Speed Literacy Errors" ~ "Retrieval Fluency",
      scale == "Naming Speed Quantity Errors" ~ "Retrieval Fluency",
      scale == "Symbol Search Rotation Errors" ~ "Response Monitoring",
      scale == "Symbol Search Set Errors" ~ "Response Monitoring",
      TRUE ~ as.character(subdomain)
    )
  )

## Narrow subdomain
table4 <-
  table4 |>
  mutate(
    narrow = case_when(
      scale == "Block Design No Time Bonus" ~ "Construction (untimed)",
      scale == "Block Design Partial Score" ~ "Construction (untimed)",
      scale == "Digit Span Forward" ~ "Verbal Attention",
      scale == "Digit Span Backward" ~ "Verbal Working Memory",
      scale == "Digit Span Sequencing" ~ "Verbal Working Memory",
      scale == "Cancellation Random" ~ "Processing Speed",
      scale == "Cancellation Structured" ~ "Processing Speed",
      TRUE ~ as.character(narrow)
    )
  )

table5 <-
  table5 |>
  mutate(
    narrow = case_when(
      scale == "Block Design Dimension Errors" ~ "Visuoconstruction",
      scale == "Block Design Rotation Errors" ~ "Visuoconstruction",
      scale == "Coding Rotation Errors" ~ "Nonverbal Processing Speed",
      scale == "Longest Digit Span Forward" ~ "Verbal Attention",
      scale == "Longest Digit Span Backward" ~ "Verbal Working Memory",
      scale == "Longest Digit Span Sequence" ~ "Verbal Working Memory",
      scale == "Longest Letter-Number Sequence" ~ "Verbal Working Memory",
      scale == "Longest Picture Span Response" ~ "Nonverbal Working Memory",
      scale == "Longest Picture Span Stimulus" ~ "Nonverbal Working Memory",
      scale == "Naming Speed Literacy Errors" ~ "Verbal Processing Speed",
      scale == "Naming Speed Quantity Errors" ~ "Verbal Processing Speed",
      scale == "Symbol Search Rotation Errors" ~ "Nonverbal Processing Speed",
      scale == "Symbol Search Set Errors" ~ "Nonverbal Processing Speed",
      TRUE ~ as.character(narrow)
    )
  )

# PASS Model
table4 <-
  table4 |>
  mutate(
    pass = case_when(
      scale == "Block Design No Time Bonus" ~ "Simultaneous",
      scale == "Block Design Partial Score" ~ "Simultaneous",
      scale == "Cancellation Random" ~ "Attention",
      scale == "Cancellation Structured" ~ "Attention",
      scale == "Digit Span Forward" ~ "Attention",
      scale == "Digit Span Backward" ~ "Sequential",
      scale == "Digit Span Sequencing" ~ "Sequential",
      TRUE ~ as.character(pass)
    )
  )

table5 <-
  table5 |>
  mutate(
    pass = case_when(
      scale == "Block Design Dimension Errors" ~ "Simultaneous",
      scale == "Block Design Rotation Errors" ~ "Simultaneous",
      scale == "Coding Rotation Errors" ~ "Attention",
      scale == "Longest Digit Span Backward" ~ "Sequential",
      scale == "Longest Digit Span Forward" ~ "Attention",
      scale == "Longest Digit Span Sequence" ~ "Sequential",
      scale == "Longest Letter-Number Sequence" ~ "Sequential",
      scale == "Longest Picture Span Response" ~ "Attention",
      scale == "Longest Picture Span Stimulus" ~ "Attention",
      scale == "Naming Speed Literacy Errors" ~ "Sequential",
      scale == "Naming Speed Quantity Errors" ~ "Sequential",
      scale == "Symbol Search Rotation Errors" ~ "Attention",
      scale == "Symbol Search Set Errors" ~ "Attention",
      TRUE ~ as.character(pass)
    )
  )

# Verbal/Nonverbal
table4 <-
  table4 |>
  mutate(
    verbal = case_when(
      scale == "Block Design No Time Bonus" ~ "Nonverbal",
      scale == "Block Design Partial Score" ~ "Nonverbal",
      scale == "Cancellation Random" ~ "Nonverbal",
      scale == "Cancellation Structured" ~ "Nonverbal",
      scale == "Digit Span Backward" ~ "Verbal",
      scale == "Digit Span Forward" ~ "Verbal",
      scale == "Digit Span Sequencing" ~ "Verbal",
      TRUE ~ as.character(verbal)
    )
  )

table5 <-
  table5 |>
  mutate(
    verbal = case_when(
      scale == "Block Design Dimension Errors" ~ "Nonverbal",
      scale == "Block Design Rotation Errors" ~ "Nonverbal",
      scale == "Coding Rotation Errors" ~ "Nonverbal",
      scale == "Longest Digit Span Backward" ~ "Verbal",
      scale == "Longest Digit Span Forward" ~ "Verbal",
      scale == "Longest Digit Span Sequence" ~ "Verbal",
      scale == "Longest Letter-Number Sequence" ~ "Verbal",
      scale == "Longest Picture Span Response" ~ "Nonverbal",
      scale == "Longest Picture Span Stimulus" ~ "Nonverbal",
      scale == "Naming Speed Literacy Errors" ~ "Verbal",
      scale == "Naming Speed Quantity Errors" ~ "Verbal",
      scale == "Symbol Search Rotation Errors" ~ "Nonverbal",
      scale == "Symbol Search Set Errors" ~ "Nonverbal",
      TRUE ~ as.character(verbal)
    )
  )

# Timed vs untimed
table4 <-
  table4 |>
  mutate(
    timed = case_when(
      scale == "Block Design No Time Bonus" ~ "Untimed",
      scale == "Block Design Partial Score" ~ "Untimed",
      scale == "Cancellation Random" ~ "Timed",
      scale == "Cancellation Structured" ~ "Timed",
      scale == "Digit Span Backward" ~ "Untimed",
      scale == "Digit Span Forward" ~ "Untimed",
      scale == "Digit Span Sequencing" ~ "Untimed",
      TRUE ~ as.character(timed)
    )
  )

table5 <-
  table5 |>
  mutate(
    timed = case_when(
      scale == "Block Design Dimension Errors" ~ "Timed",
      scale == "Block Design Rotation Errors" ~ "Timed",
      scale == "Coding Rotation Errors" ~ "Timed",
      scale == "Longest Digit Span Backward" ~ "Untimed",
      scale == "Longest Digit Span Forward" ~ "Untimed",
      scale == "Longest Digit Span Sequence" ~ "Untimed",
      scale == "Longest Letter-Number Sequence" ~ "Untimed",
      scale == "Longest Picture Span Response" ~ "Untimed",
      scale == "Longest Picture Span Stimulus" ~ "Untimed",
      scale == "Naming Speed Literacy Errors" ~ "Timed",
      scale == "Naming Speed Quantity Errors" ~ "Timed",
      scale == "Symbol Search Rotation Errors" ~ "Timed",
      scale == "Symbol Search Set Errors" ~ "Timed",
      TRUE ~ as.character(timed)
    )
  )
```

```{r}
# Description
table4 <-
  table4 |>
  mutate(
    description = case_when(
      scale == "Block Design No Time Bonus" ~ "Visuoconstruction and integration of blocks (untimed)",
      scale == "Block Design Partial Score" ~ "Visuoconstruction and integration of blocks (total correct)",
      scale == "Digit Span Backward" ~ "Recall of digits backward",
      scale == "Digit Span Forward" ~ "Recall of digits forward",
      scale == "Digit Span Sequencing" ~ "Recall of digits sequentially",
      scale == "Cancellation Random" ~ "Unstructured selective visual attention",
      scale == "Cancellation Structured" ~ "Structured selective visual attention",
      TRUE ~ as.character(description)
    )
  )

table5 <-
  table5 |>
  mutate(
    description = case_when(
      scale == "Block Design Dimension Errors" ~ "visuoconstruction and integration of blocks (dimension errors)",
      scale == "Block Design Rotation Errors" ~ "visuoconstruction and integration of blocks (rotation errors)",
      scale == "Longest Digit Span Forward" ~ "Auditory attention span",
      scale == "Longest Digit Span Backward" ~ "Working memory span",
      scale == "Longest Digit Span Sequence" ~ "Working memory span (sequencing)",
      scale == "Longest Letter-Number Sequence" ~ "Recalling and reordering progressively longer series of digits and letters",
      scale == "Symbol Search Rotation Errors" ~ "Processing speed, attention, and concentration (rotation errors)",
      scale == "Symbol Search Set Errors" ~ "Processing speed, attention, and concentration (set errors)",
      scale == "Naming Speed Literacy Errors" ~ "naming speed for objects/letters/numbers (errors)",
      scale == "Naming Speed Quantity Errors" ~ "naming speed for quantities (errors)",
      scale == "Longest Picture Span Response" ~ "Visual/nonverbal working memory and working memory capacity (response)",
      scale == "Longest Picture Span Stimulus" ~ "Visual/nonverbal working memory and working memory capacity (stimulus)",
      scale == "Coding Rotation Errors" ~ "Visual-motor processing speed (rotation errors)",
      TRUE ~ as.character(description)
    )
  )  
```

## Glue result

```{r}
table4 <-
    table4 |> 
    tidytable::mutate(
      result = glue::glue(
        "{description} was {range}."
      )
    )

table5 <-
    table5 |> 
    tidytable::mutate(
      result = glue::glue(
        "{description} was {range}."
      )
    )


## Relocate variables
table4 <- table4 |> dplyr::relocate(c(raw_score, score, ci_95, percentile, range), .after = scale)
table4 <- table4 |> dplyr::relocate(c(test, test_name), .before = scale)

table5 <- table5 |> dplyr::relocate(c(raw_score), .after = scale)
table5 <- table5 |> dplyr::relocate(c(test, test_name), .before = scale)
```

# Combine tables

```{r}
wisc5 <- collapse::rowbind(table2, table3, table1, table4, table5, fill = TRUE)
```

## Write out final csv

```{r}
readr::write_csv(wisc5, here::here("data", "csv", "wisc5.csv"))
```
